---
title: "HW 01 - Earthquakes"
author: "Vincent Baker"
date: "1/30/23"
output: github_document
---

## Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

There are 123 earthquakes in the dataset.

### Exercise 2

There are 7 variables in the dataset. 

### Exercise 3

```{r}
earthquakes %>%
  count(region, sort = TRUE)
```

Turkey, Iran, and China have experienced the most notable earthquakes in the 20th century. 

### Exercise 4

```{r earthquakes-top10, eval=TRUE}
earthquakes %>%
  count(richter, sort = TRUE) %>%
  slice_max(n, n = 5)
arrange(earthquakes, richter, .by_group = TRUE)
```
This dataset is now arranged by the Richter Scale (earthquake intensity).

### Exercise 5

There seems to be no relationship between the earthquake magnitude and year of the 20th century. The data shows that magnitude varies throughout the 20th century and many of the values are close to Magnitude 7. 

### Exercise 6

You could probably predict the death toll by just the earthquake magnitude, but that alone might not be very reliable because, for example, Peru experienced a Magnitude 8 earthquake and had a high death toll around the late 60s, but if you look at China, the earthquake after 1925 created far less casualties than the one after 1975, and both experienced closed to a Magnitude 7.5 earthquake. 

### Exercise 7

The final visualization makes me feel less confident about earthquake magnitude and death toll because, again, China experienced Magnitude 7.5 and one >7.5 earthquakes, and the one that was greater had less casualties. 
